### 2021-11-26 Complexity/UGC/hastad.tex
pretty much finished draft of ugc writeup

Note that if the labels assigned $a,b$ satisfied $\pi$ and $f_a,f_b$ are valid long codes: $f_a(x \circ \pi) = f_b(x )$ for all $x \in \{-1,1\}^{|\Sigma_B|}$.

@@

\subsection{Folded Functions}

>>>>

First, note that if the labels assigned $a,b$ satisfied $\pi$ and $f_a,f_b$ are valid long codes: $f_a(x \circ \pi) = f_b(x )$ for all $x \in \{-1,1\}^{|\Sigma_B|}$. Second, Step 4 of the verfier can be expressed as a three variable linear equation:

\begin{equation} \label{hastadpred}
 f_a(z) f_b(x)f_a(y) = 1
\end{equation}

@@

\subsection{Folded Functions}
A technical detail requires that functions queried $f_a,f_b$ be \emph{folded} in the sense that:
%
\begin{definition}
A boolean function $f:\{-1,1\}^n \rightarrow \{-1,1\}$ is said to be folded if for every $x \in \{-1,1\}$, $f(-x) = -f(x)$.
\end{definition}

These functions are also said to \emph{odd}. It can be shown that \emph{folded} functions have their Fourier weights concentrated on subsets of odd cardinality. In particular, for boolean function $f$ folded: $\widehat{f}(\emptyset) = 0$. Why would we need this property? One issue that arises with the predicates shown in Equation \ref{hastadpred} is when all functions are simply the constant function $f_a = f_b = 1$. This passes the test with probability one. This can be avoided by restricting the functions to be folded. Of course, dictator functions are folded. Furthermore, we do not need to increase the number of queries to enforce this requirement: for any two pair of queries $(x,-x)$ and a queried function $f$, if the test queries $f(x)$, the value $f(-x)$ can be subsequently computed as $-f(x)$.

### 2021-11-26 Complexity/UGC/labelcover.tex
Grammar and additions to pcp section
pretty much finished draft of ugc writeup

%\subsection{}
%Arora, Barak
\subsection{Some Structural Results of PCPs}

\subsection{Raz's Parallel Repetition Theorem}

@@

>>>>

%\subsection{}
%Arora, Barak

\subsection{Raz's Parallel Repetition Theorem}
In this section, we give a cursory outline of Raz's Parallel Repetition Theorem and its consequences. First, we can extend Definition \ref{pcpdef} to include proof strings over non-boolean alphabets.
%
To accomdate such verifiers, we can extend the definition to $\PCP^\Sigma_{\beta, \alpha}(r(n),q(n))$, the class of languages with polynomial-time verifiers taking proof strings $\pi$ over non-boolean alphabet $\Sigma$ and uses $r(n)$ random bits and at most $q(n)$ queries to $\pi$.
%
The following theorem shows that one can reduce the number of queries to two at the expense of a weaker soundness constant:
%
\begin{theorem} \label{2queryinclusion}
  $\PCP^\Sigma_{1 - \alpha, 1}(r(n),q(n)) \subseteq \PCP^{\Sigma^q}_{1 - \frac{\alpha}{q},1}(r(n) + \log{q(n)}, 2)$
\end{theorem}
%
\begin{proof}
Given a verifier for a language $L \in \PCP^\Sigma_{\beta, 1 - \alpha}(r(n),q(n))$, it behaves as such on input $x \in \{0,1\}^n$:
%
\begin{enumerate}
  \item Flips a $r(n)$ coins which we denote as $R$.
  \item Using $R$, it computes a series of indices $i_1, \cdots i_q$ where $q = q(n)$.
  \item It queries $\pi_{i_1}, \cdots \pi_{i_q}\in \Sigma$ from the proof $\pi$.
  \item Finally, it feeds the symbols in a predicate $V_{x,R}(\pi_{i_1}, \cdots \pi_{i_q})$ which outputs ``accept" or ``reject".
\end{enumerate}
We extend this to a modified verfier $V'$ to accomodate the concatenation of two proof strings: if $m = |\Sigma|$ $\pi_1:[m]^q$ then $\rightarrow \Sigma^{q}$ and $\pi_2:[m]\rightarrow \Sigma$:
%
\begin{enumerate}
  \item Flips a $r(n)$ coins which we denote as $R$.
  \item Using $R$, it computes a series of indices $i_1, \cdots i_q$ where $q = q(n)$
  \item Queries $\pi' = \pi_1(i_1, \cdots, i_q)$
  \item Computes the predicate:
  \[ V_{x,R}'(\pi') = V_{x,R}(\pi'_1,\cdots,\pi'_q) \]
  \item Finally, chooses random $\ell \in [q]$ and checks if $\pi_2(i_\ell) = \pi'_\ell$.
  \item The verifier accepts iff both checks pass.
\end{enumerate}

For completeness, if there exists a proof $\pi$ which the original verifier $V$ accepts with probability one, then setting $\pi_1(i_1, \cdots, i_q) = (\pi_{i_1},\cdots,\pi_{i_q})$ and $\pi_2 = \pi$ will induce $V'$ to accept with probability one by construction.
%
As for soundness, suppose  at least $\alpha$ fraction of the predicates $V_{x,R}$ reject in respect to some proof string $\pi$. Each one of the predicates contained in this fraction must fail the check at Step $4$ if $\pi' = \pi_1(i_1, \cdots, i_q) = (\pi_{i_1},\cdots,\pi_{i_q})$. However, $\pi_1$ does not have to respect this rule for any $q$-tuple of queries $(i_1, \cdots, i_q)$ given as input. If so, there must exist at least one index $\ell$ such that $\pi'_\ell \neq \pi_2(i_\ell) = \pi_\ell$. Since such an index is chosen with probability $\frac{1}{q}$, we have that $V'$ must reject with probability at least $\frac{\alpha}{q}$. This completes the proof. 
\end{proof}

%
Raz's Parallel Repetition Theorem constructed a verifier which allowed the soundness constant to drop exponentially with the cost of bloating the alphabet size:
\begin{theorem} (Raz's Parallel Repetition Theorem \ref{raz1998parallel}) \label{razparallelrep}
  For all $s \in (0,1)$, there exists $c_s \in (0,s)$ such that:
    \[ \PCP^{\Sigma}_{s,1}(r,2) \subseteq \PCP^{\Sigma^t}_{c_s^t,1}(rt,2)  \]
\end{theorem}

\begin{corollary} \label{razcorollary} For all $\epsilon > 0$, there exists an alphabet $\Sigma$ such that $|\Sigma| \leq \mathsf{poly}(\frac{1}{\epsilon})$:
  $$ \NP \subseteq \PCP^{\Sigma}_{\epsilon,1}(O(\log{n}\cdot\log{1/\epsilon}),2) $$
\end{corollary}
%
\begin{proof}
  For some constant $Q > 0$,
  \begin{align*}
    \NP & \subseteq \PCP_{\frac{1}{2},1}^{\{0,1\}}(O(\log{n}), Q) \\
    & \subseteq \PCP_{1- \frac{1}{2Q},1}^{\{0,1\}^Q}(O(\log{n}), 2) \\
    & \subseteq \PCP_{c_Q^t,1}^{\{0,1\}^{Qt}}(O(t\log{n}), 2) \\
    & \subseteq   \PCP_{\epsilon,1}^{\Sigma}(O(\log{n}\cdot\log{1/\epsilon}), 2)
  \end{align*}
  where $|\Sigma| \leq \mathsf{poly}(\frac{1}{\epsilon})$. The second inclusion follows from Theorem \ref{2queryinclusion} and the third inclusion follows from Theorem \ref{razparallelrep}.
\end{proof}

By combining Corollary \ref{razcorollary}, the $\NP$-hardness of Label Cover comes to fruition:

@@

This is shown by embedding the query pairs of the verifier into the projection constraints of a Label Cover instance graph.

### 2021-11-26 Complexity/UGC/pcp.tex
pretty much finished draft of ugc writeup

\begin{definition}
  Given a language $L$ and $r,q: \mathbb{N} \rightarrow \mathbb{N}$, a \emph{(r(n),q(n))-$\PCP$-verifier} for $L$ consists of a polynomial-time algorithm $V$ with the following properties: \newline

@@

\begin{remark}
  Sometimes the completeness criterion is too strong for our purposes (see the comments on $\ELin$ problem). In these cases, we like to denote the class $\PCP_{\beta, \alpha}(r(n),q(n))$ as the languages $L$ which have a $(r(n),q(n))$-$\NP$-verifier such that the completeness and soundness criteria are amended as below: \newline

@@

    \item (Soundness) For $x \not\in L$, for all proofs $\pi$:
    %
    \begin{equation}
      \mathbb{P}_{r}[V(x,\pi,r) = 1] \leq \alpha
    \end{equation}
  \end{itemize}
Here, $\beta$ is the \emph{completeness parameter} while $\alpha$ is the \emph{soundness parameter}. The class introduced in the original definition would thus be denoted as $\PCP_{1,\frac{1}{2}}(r(n),q(n))$. PCP verifiers whose completeness parameter is one ($\beta = 1$) is deemed as \emph{perfectly complete}.
\end{remark}

The PCP Theorem says that $\NP$ is \emph{exactly} the class of PCPs which uses a \emph{logarithmic} number of random bits and a \emph{constant} number of queries.
%
\begin{theorem} \label{pcptheorem} (The $\PCP$ Theorem \cite{arora1998proof}, \cite{arora1998probabilistic})
%
\begin{equation}
\NP = \PCP_{1,\frac{1}{2}}(O(\log{n}), O(1))
\end{equation}
\end{theorem}

@@

\begin{proposition}
For every constants $Q \in \mathbb{N}, c > 0$, $\PCP_{1,\frac{1}{2}}(c\cdot\log{n}, Q) \subseteq \NP$
\end{proposition}

\begin{proof}
Begin with the observation that $\PCP_{1,\frac{1}{2}}(r(n), q(n)) \subseteq \NTIME(q(n)2^{r(n)})$. This is justified by the view of an $\NTIME$ machine simulating the verifier by trying all possible coin tosses and queries to the input string $x$ and proof string $\pi$. It can then count all of the accepting paths to determine the probability of acceptance. If $q = O(1)$ and $r = O(\log{n})$, then the right side of the inclusion will be $\NTIME(2^{O(\log{n})}) = \NP$.
\end{proof}

@@

\begin{theorem} \label{pcptheoremgapcsp}  ($\PCP$-Theorem: $\mathsf{GapMaxCSP}$- hardness) There exists constants $q \in \mathbb{N}$ and $\alpha \leq 1$ where the problem $\mathsf{Gap}_{\alpha,1}\mathsf{Max}$-$\mathsf{qCSP}$ is $\NP$-hard. To elaborate, for every $\NP$ language $L$, there exists a polynomial time reduction mapping an $L$ to a instance $f(x)$ of some CSP $\Psi$ over domain $\Omega=\{0,1\}$ where $\Psi$ consists of $q$-ary predicates, such that

@@

\begin{proof}
First, assume $\NP = \PCP_{1,\frac{1}{2}}(O(\log{n}), O(1))$. We will outline a procedure to convert the verifier $V$ into an instance $\I$ for a $q$-ary CSP $\Psi$ for some constant $q$. For some input string $x \in \{0,1\}^n$ and proof string $\pi$, let $r \in \{0,1\}^{c \cdot \log{n}}$ be the coin flips made by $V$ and $V_{x,r}$ be the deterministic procedure which is executed on input $x$ and coin flip $r$ such that $V_{x,r} = 1$ iff $V$ accepts proof $\pi$ on input $x$ and coin flip $r$. We can define the domain of our constructed CSP $\Psi$ to be $\Omega=\{0,1\}$ and the predicates to be $\{V_{x,r}\}_{r}$. Now our instance $\I$ of $\Psi$ is casted as the tuples $(S, V_{x,r})$ where $S$ will be at most a $q$-sized tuple indicating which indices of the proof $\pi$ are queried when conditioned on $r$. This yields a polynomially-sized $\mathsf{qCSP}$ instance $\I$. Furthermore, since the verifier $V$ runs in polynomial time, it's execution can be simulated on all $r$ to output the instance $\I$ in polynomial-time. Thus, we have given a polynomial-time reduction from an input $x$ to its corresponding CSP instance $\I$, so Theorem \ref{pcptheoremgapcsp}. \newline

Conversely, suppose we had a reduction from $\NP$ to $\mathsf{Gap}_{\alpha,1}\mathsf{Max}$-$\mathsf{qCSP}$ as stated in Theorem \ref{pcptheoremgapcsp}. We devise polynomial-time reduction taking an instance $\mathsf{Max}$-$\mathsf{qCSP}$ to a polynomial-time PCP verifier $V$ using logarithmic number of random bits and a constant number of queries to the supplied proof $\pi$. For an input $x \in \{0,1\}^n$, the proof will be expected to be an assignment to its respective instance $f(x)$ in the notation utilized in Theorem \ref{pcptheoremgapcsp}. Verifier $V$ makes coin flips $r \in \{0,1\}^{c\log{n}}$ to choose one constraint tuple $(S,\psi)$ where $\psi$ is some $q$-ary predicate. Only a logarithmic number of random bits are required to query any constraint in instance $f(x)$ as the polynomial-time $\NP$ reduction can only generate a polynomial number of such constraints.  The PCP only has to make $q$-queries to the proof $\pi$ to find the assignments to the variables listed in $S = (v_1,\cdots,v_q)$. By the properties listed in Theorem \ref{pcptheoremgapcsp}, the PCP verifier $V$ must have completeness $1$ and soundness $\leq \frac{1}{2}$ as claimed.
\end{proof}

\begin{lemma} (Equivalnce between $\mathsf{GapMaxCSP}$and $\mathsf{GapMax3SAT}$ Theorem \ref{pcpgapsat} and Theorem \ref{pcptheoremgapcsp} are equivalent.
\end{lemma}
%
\begin{proof}
Since any $\mathsf{3Sat}$ instance can be seen as a particular type of $\mathsf{3CSP}$ instance, one direction is immediate. Conversely, if we assume Theorem \ref{pcptheoremgapcsp}, we aim to find some constant $\alpha'$ such that there exist a reduction from an instance of $\mathsf{Gap}_{1-\alpha,1}\mathsf{Max}$-$\mathsf{qCSP}$ for $q \in \mathbb{N}$ claimed in Theorem \ref{pcptheoremgapcsp} to an instance of $\mathsf{Gap}_{1-\alpha',1}\mathsf{Max3Sat}$.
%
Let the CSP $\Psi$ be comprised $q$-ary predicates $\psi$. For an instance $\I$ of $\Psi$, an constraint tuple $(S,\psi)$ can be expressed as a logical AND of $2^q$ clauses where each clause is a logical OR of $q$ variables or their negations. In other words, $(S,\psi)$ is essentially a CNF of width $q$ and of size at most $2^q$. We can then construct an ``equivalent" 3CNF as follows: add extra symbols $\Pi_{1}, \cdots, \Pi_{(q-3)2^{q}}$. It can be shown that there exists a 3CNF $\psi'_S$ of size at most $(q-2)2^{q}$ such that:

@@

>>>>

\begin{definition} \ref{pcpdef}
  Given a language $L$ and $r,q: \mathbb{N} \rightarrow \mathbb{N}$, a \emph{(r(n),q(n))-$\PCP$-verifier} for $L$ consists of a polynomial-time algorithm $V$ with the following properties: \newline

@@

\begin{remark}
  Sometimes the completeness criterion is too strong for our purposes (see the comments on $\ELin$ problem). In these cases, we like to denote the class $\PCP_{\alpha, \beta }(r(n),q(n))$ as the languages $L$ which have a $(r(n),q(n))$-$\NP$-verifier such that the completeness and soundness criteria are amended as below: \newline

@@

    \item (Soundness) For $x \not\in L$, for all proofs $\pi$:
    %
    \begin{equation}
      \mathbb{P}_{r}[V(x,\pi,r) = 1] \leq \alpha
    \end{equation}
  \end{itemize}
Here, $\beta$ is the \emph{completeness parameter} while $\alpha$ is the \emph{soundness parameter}. The class introduced in the original definition would thus be denoted as $\PCP_{\frac{1}{2},1}(r(n),q(n))$. PCP verifiers whose completeness parameter is one ($\beta = 1$) is deemed as \emph{perfectly complete}.
\end{remark}

The PCP Theorem says that $\NP$ is \emph{exactly} the class of PCPs which uses a \emph{logarithmic} number of random bits and a \emph{constant} number of queries.
%
\begin{theorem} \label{pcptheorem} (The $\PCP$ Theorem \cite{arora1998proof}, \cite{arora1998probabilistic})
%
\begin{equation}
\NP = \PCP_{frac{1}{2},1}(O(\log{n}), O(1))
\end{equation}
\end{theorem}

@@

\begin{proposition}
For every constants $Q \in \mathbb{N}, c > 0$, $\PCP_{\frac{1}{2}, 1}(c\cdot\log{n}, Q) \subseteq \NP$
\end{proposition}

\begin{proof}
Begin with the observation that $\PCP_{\frac{1}{2},1}(r(n), q(n)) \subseteq \NTIME(q(n)2^{r(n)})$. This is justified by the view of an $\NTIME$ machine simulating the verifier by trying all possible coin tosses and queries to the input string $x$ and proof string $\pi$. It can then count all of the accepting paths to determine the probability of acceptance. If $q = O(1)$ and $r = O(\log{n})$, then the right side of the inclusion will be $\NTIME(2^{O(\log{n})}) = \NP$.
\end{proof}

@@

\begin{theorem} \label{pcptheoremgapcsp}  ($\PCP$-Theorem: $\mathsf{GapMaxqCSP}$- hardness) There exists constants $q \in \mathbb{N}$ and $\alpha \leq 1$ where the problem $\mathsf{Gap}_{\alpha,1}\mathsf{MaxqCSP}$ is $\NP$-hard. To elaborate, for every $\NP$ language $L$, there exists a polynomial time reduction mapping an $L$ to a instance $f(x)$ of some CSP $\Psi$ over domain $\Omega=\{0,1\}$ where $\Psi$ consists of $q$-ary predicates, such that

@@

\begin{proof}
First, assume $\NP = \PCP_{\frac{1}{2},1}(O(\log{n}), O(1))$. We will outline a procedure to convert the verifier $V$ into an instance $\I$ for a $q$-ary CSP $\Psi$ for some constant $q$. For some input string $x \in \{0,1\}^n$ and proof string $\pi$, let $r \in \{0,1\}^{c \cdot \log{n}}$ be the coin flips made by $V$ and $V_{x,r}$ be the deterministic procedure which is executed on input $x$ and coin flip $r$ such that $V_{x,r} = 1$ iff $V$ accepts proof $\pi$ on input $x$ and coin flip $r$. We can define the domain of our constructed CSP $\Psi$ to be $\Omega=\{0,1\}$ and the predicates to be $\{V_{x,r}\}_{r}$. Now our instance $\I$ of $\Psi$ is casted as the tuples $(S, V_{x,r})$ where $S$ will be at most a $q$-sized tuple indicating which indices of the proof $\pi$ are queried when conditioned on $r$. This yields a polynomially-sized $\mathsf{qCSP}$ instance $\I$. Furthermore, since the verifier $V$ runs in polynomial time, it's execution can be simulated on all $r$ to output the instance $\I$ in polynomial-time. Thus, we have given a polynomial-time reduction from an input $x$ to its corresponding CSP instance $\I$, so Theorem \ref{pcptheoremgapcsp}. \newline

Conversely, suppose we had a reduction from $\NP$ to $\mathsf{Gap}_{\alpha,1}\mathsf{MaxqCSP}$ as stated in Theorem \ref{pcptheoremgapcsp}. We devise polynomial-time reduction taking an instance $\mathsf{MaxqCSP}$ to a polynomial-time PCP verifier $V$ using logarithmic number of random bits and a constant number of queries to the supplied proof $\pi$. For an input $x \in \{0,1\}^n$, the proof will be expected to be an assignment to its respective instance $f(x)$ in the notation utilized in Theorem \ref{pcptheoremgapcsp}. Verifier $V$ makes coin flips $r \in \{0,1\}^{c\log{n}}$ to choose one constraint tuple $(S,\psi)$ where $\psi$ is some $q$-ary predicate. Only a logarithmic number of random bits are required to query any constraint in instance $f(x)$ as the polynomial-time $\NP$ reduction can only generate a polynomial number of such constraints.  The PCP only has to make $q$-queries to the proof $\pi$ to find the assignments to the variables listed in $S = (v_1,\cdots,v_q)$. By the properties listed in Theorem \ref{pcptheoremgapcsp}, the PCP verifier $V$ must have completeness $1$ and soundness $\leq \frac{1}{2}$ as claimed.
\end{proof}

\begin{lemma} (Equivalnce between $\mathsf{GapMaxqCSP}$and $\mathsf{GapMax3SAT}$ Theorem \ref{pcpgapsat} and Theorem \ref{pcptheoremgapcsp} are equivalent.
\end{lemma}
%
\begin{proof}
Since any $\mathsf{3Sat}$ instance can be seen as a particular type of $\mathsf{3CSP}$ instance, one direction is immediate. Conversely, if we assume Theorem \ref{pcptheoremgapcsp}, we aim to find some constant $\alpha'$ such that there exist a reduction from an instance of $\mathsf{Gap}_{1-\alpha,1}\mathsf{MaxqCSP}$ for $q \in \mathbb{N}$ claimed in Theorem \ref{pcptheoremgapcsp} to an instance of $\mathsf{Gap}_{1-\alpha',1}\mathsf{Max3Sat}$.
%
Let the CSP $\Psi$ be comprised $q$-ary predicates $\psi$. For an instance $\I$ of $\Psi$, an constraint tuple $(S,\psi)$ can be expressed as a logical AND of $2^q$ clauses where each clause is a logical OR of $q$ variables or their negations. In other words, $(S,\psi)$ is essentially a CNF of width $q$ and of size at most $2^q$. We can then construct an ``equivalent" 3CNF $\psi'_S$ as follows: add extra symbols $\Pi_{1}, \cdots, \Pi_{(q-3)2^{q}}$. It can be shown that there exists a 3CNF $\psi'_S$ of size at most $(q-2)2^{q}$ such that:

@@

\begin{remark}
  The existence of the ``equivalent" 3CNF is outlined in Problem 7.11 of the O'Donnell textbook \cite{o2014analysis}.
 \end{remark}

\begin{remark}
The proof of the PCP Theorem (Theorem \ref{pcptheorem}) is quite involved and out of the scope of these notes. The original proof hinged on clever algebraic techniques such as low-degree testing \cite{arora1998probabilistic}. A simpler combinatorial proof by Dinur arrived years later  \cite{dinur2007pcp}. For more information, refer to the cited publications or Chapter 22 of the Arora, Barak textbook \cite{arora2009computational}.
\end{remark}

### 2021-11-26 Complexity/UGC/ugcmaxcut.tex
Yet more touches to UGC paper
Grammar and additions to pcp section
pretty much finished draft of ugc writeup

\begin{theorem}
  $\mathsf{Gap}_{\alpha,\beta}\mathsf{MaxCut}$ is $\UG$-hard iff there exists a constant $\delta > 0$ such that for all $m$ there exists a 2-query PCP for $\mathsf{Gap}_{\delta, 1-\delta}\ULC$ with completeness $\beta$ and soundness $\alpha$.
\end{theorem}
%
\begin{proof}
  First assume that for some $\delta > 0$ and all $m$, there exists a polynomial-time reduction from $\GapDeltaULC$ to $\mathsf{Gap}_{\alpha,\beta}\mathsf{MaxCut}$. Let $G=(V,E), \mathcal{C}$ be the graph outputted by reduction and the cut outputted by the cut approximation algorithm. Construct a PCP samples two vertices from $v_1, v_2 \sim V$ by querying the proof tape encoding $G,\mathcal{C}$ and outputs ``accept" if $(v_1,v_2) \in \mathcal{C}$. The completeness and soundness parameters immediately follow from definition of $\mathsf{Gap}_{\alpha,\beta}\mathsf{MaxCut}$. Conversely, assume the existance of a 2-query PCP for $\GapDeltaULC$ with the above properties. We will calculate the acceptance probabilities of this PCP given a proof string and an input instance by finding the max cut. Let the vertices be the proof locations of the input proof string $\pi$. It suffcies to draw an edge between two vertices weighted by the probability their corresponding proof locations are queried by the verifier.
\end{proof}

@@

%
%
%
\subsection{Dictatorship Testing Redux}

%
%
%
\subsection{Majority is the Stablest (MIS)}
%
Before we craft our dictator test, we require a tool bounding the noise sensitivity of a boolean function with small low-degree influence. This is captured by the ``Majority is the Stablest" theorem:

@@

A generalization of the MIS theorem will serve our purposes:

@@

%
%
%
\subsection{The 2-query PCP}
With the MIS theorem, we can begin our analysis of the promised 2-query PCP. Before the procedure, define $(x \circ \pi)_i = x_{\pi(i)}$ for $x \in \{-1,1\}^n, \; i \in [n], \; \pi \in S_n$.  \newline

@@

Through a Fourier-analytic argument, we can upper-bound $|S_b|$:
\begin{align*}
  \frac{|S_b|\tau}{2} \leq \sum_{i = 1}^{|S_b|} \mathsf{Inf}_i^{\leq d}(f_b) \leq \sum_{i = 1}^m \mathsf{Inf}_i^{\leq d}(f_b) = \sum_{\overset{S \subseteq [m]}{|S| \leq d}} |S| \hat{f}^2(S) \leq d \sum_{S \subseteq [m]}  \hat{f}^2(S) = d
\end{align*}
This yields that $|S_b| \leq \frac{2d}{\tau}$. So the probability bound of \ref{probbound} would become:
%
\begin{equation}
  \mathbb{P}[\pi_{(b,a)} \text{ is satisfied}] \geq \frac{\epsilon}{2}\frac{\tau}{2}\frac{\tau}{2d} = \frac{\epsilon\tau^2}{8d} = \delta
\end{equation}
as desired. This completes the proof of Theorem \ref{maxcutughard}.

\end{proof}

>>>>

\begin{theorem}
  $\mathsf{Gap}_{\alpha,\beta}\mathsf{MaxCut}$ is $\UG$-hard iff there exists a constant $\delta > 0$ such that for all $m$ there exists a 2-query PCP for $\mathsf{Gap}_{\delta, 1-\delta}\ULC$ with completeness $\beta$ and soundness $\alpha$.
\end{theorem}
%
\begin{proof}
  First assume that for some $\delta > 0$ and all $m$, there exists a polynomial-time reduction from $\GapDeltaULC$ to $\mathsf{Gap}_{\alpha,\beta}\mathsf{MaxCut}$. Let $G=(V,E), \mathcal{C}$ be the graph outputted by reduction and the cut outputted by the cut approximation algorithm. Construct a PCP samples two vertices from $v_1, v_2 \sim V$ by querying the proof tape encoding $G,\mathcal{C}$ and outputs ``accept" if $(v_1,v_2) \in \mathcal{C}$. The completeness and soundness parameters immediately follow from definition of $\mathsf{Gap}_{\alpha,\beta}\mathsf{MaxCut}$. Conversely, assume the existence of a 2-query PCP for $\GapDeltaULC$ with the above properties. We will calculate the acceptance probabilities of this PCP given a proof string and an input instance by finding the max cut. Let the vertices be the proof locations of the input proof string $\pi$. It suffices to draw an edge between two vertices weighted by the probability their corresponding proof locations are queried and accepted by the verifier.
\end{proof}

@@

%
%
%
\subsection{Dictatorship Testing and Majority is the Stablest (MIS)}
A key difference between dictatorship test crafted in H\aa stad's 3-bit PCP for $\NP$ and the one will aim to utilize here is the number of queries the PCP can make. Namely, the reduction here can only use \emph{two} queries to the proof rather than the three queries afforded to H\aa satd's verifier. The dictatorship test we will focus on for this reduction utilizes only two queries to the functions: given input boolean function $f:\{-1,1\}^n \rightarrow \{-1,1\}$ and $\rho \in (-1,0)$:

\begin{enumerate}
  \item Sample $x \sim \{-1,1\}^n$
  \item Sample $y \sim N_{\rho}(x)$
  \item Accept iff $f(x) \neq f(y)$
\end{enumerate}
%
Before we analyze the acceptance probability of our dictatorship test, we require a tool bounding the noise sensitivity of a boolean function with small low-degree influence. This is captured by the ``Majority is the Stablest" theorem:

@@

To see the significance of the MIS Theorem, we compute the acceptance rate of the dictatorship test above:

\begin{align*}
\mathbb{P}\left[ \text{ Test Accepts }\right] & = \mathbb{E}_{x,y}\left[\frac{1}{2} - \frac{1}{2}f(x)f(y) \right] \\
& = \frac{1}{2} - \frac{1}{2}\mathbb{E}_{x,y}\left[f(x)f(y) \right] \\
& = \frac{1}{2} - \frac{1}{2}\mathsf{Stab}_\rho(f)
\end{align*}

We can now reason about acceptance probability in the context of several classes of functions:

\begin{itemize}
  \item Dictators pass the test with probabilty $\frac{1 - \rho}{2}$
  \item The parity functions $\chi_S,\; S \subseteq [n]$ pass with probability $\frac{1 - \rho^{|S|}}{2}$. As $|S|$ grows, the acceptance probability tends to $\frac{1}{2}$.
  \item Majority functions passes the test with probability approaching in the limit $\frac{\cos^{-1}(\rho)}{\pi}$.
\end{itemize}

What the MIS Theorem roughly tells us is that functions with no ``notable" coordinates, i.e all coordinates have small influence, can pass the test with probability at most $\frac{\cos^{-1}(\rho)}{\pi}$. The proof of the soundness of our verifier will exploit the observation that functions with a sufficiently large $i^{th }$ influence for some coordinate $i$ will be ``close enough" to a dictator. This property will be used to extract a labeling to the $\mathsf{UniqueLC}(m)$ instance satisfying a large fraction of constraints.

For the analysis of constructed PCP verifier, a generalization of the MIS theorem will serve our purposes:

@@

where $\mathsf{Inf}^{\leq d}_i(f)$ refers to the $i^{th}$ influence of $f$ restricted to degrees of at most $d$:

\begin{equation}
  \mathsf{Inf}^{\leq d}_i(f) = \sum_{\substack{S \subseteq [n], \; i \in S \\ |S| \leq d}} |S|
  \cdot\widehat{f}(S)^2
\end{equation}

Note that the image of our function $f$ is the contained in the closed interval $[-1,1]$ rather than the finite set $\{-1, 1\}$ as stated in the ordinary MIS theorem.
%
%
%
\subsection{The 2-query PCP}
With the MIS theorem, we can begin our analysis of the promised 2-query PCP. Before the procedure, define $(x \circ \pi)_i = x_{\pi(i)}$ for $x \in \{-1,1\}^n, \; i \in [n], \; \pi \in S_n$.  \newline

@@

Through a Fourier-analytic argument, we can upper-bound $|S_b|$:
\begin{align*}
  \frac{|S_b|\tau}{2} \leq \sum_{i = 1}^{|S_b|} \mathsf{Inf}_i^{\leq d}(f_b) \leq \sum_{i = 1}^m \mathsf{Inf}_i^{\leq d}(f_b) = \sum_{\overset{S \subseteq [m]}{|S| \leq d}} |S| \hat{f}^2(S) \leq d \sum_{S \subseteq [m]}  \hat{f}^2(S) = d
\end{align*}
This yields that $|S_b| \leq \frac{2d}{\tau}$. So the probability bound of \ref{probbound} would become:
%
\begin{equation}
  \mathbb{P}[\pi_{(b,a)} \text{ is satisfied}] \geq \frac{\epsilon}{2}\frac{\tau}{2}\frac{\tau}{2d} = \frac{\epsilon\tau^2}{8d} = \delta
\end{equation}
as desired. This completes the proof of Theorem \ref{maxcutughard}.
\end{proof}

%We showed that the test to accept with probability %larger than $\GWConstant + \epsilon$ must
